\chapter{How to cite the AFN BCs}

This is a technical non-peer-reviewed document and should not be cited directly. To cite the AFN BCs:

\begin{itemize}
    \item When implementing the AFN BCs in another code: cite at least \cite{nf_niels}.
    \item When using the AFN BCs in SOLPS-ITER code: cite at least \cite{nf_niels} and \cite{nf_wim}.
\end{itemize}

Additional papers can be cited if desired. The list below summarizes AFN contributions with a short description.

\begin{itemize}
    \item Horsten, N., Dekeyser, W., Samaey, G., Börner, P., \& Baelmans, M. (2016). Fluid neutral model for use in hybrid neutral simulations of a detached case. Contributions to Plasma Physics, 56(6‐8), 610-615. \newline \newline 
    AFN in 1D in MATLAB
    \item Horsten, N., Samaey, G., \& Baelmans, M. (2017). Development and assessment of 2D fluid neutral models that include atomic databases and a microscopic reflection model. Nuclear Fusion, 57(11), 116043. \newline \newline 
    AFN in 2D in MATLAB
    \item Blommaert, M., Dekeyser, W., Horsten, N., Börner, P., \& Baelmans, M. (2018). Implementation of a consistent fluid‐neutral model in SOLPS‐ITER and benchmark with EIRENE. Contributions to Plasma Physics, 58(6-8), 718-724. \newline \newline 
    Implementation of the AFN model in the structured version of SOLPS-ITER and first benchmarks with EIRENE on slab cases. Consistency with EIRENE pumping mechanism. First use of the Maxwellian approach for the radial boundaries.
    \item Van Uytven, W., Blommaert, M., Dekeyser, W., Horsten, N., \& Baelmans, M. (2020). Implementation of a separate fluid‐neutral energy equation in SOLPS‐ITER and its impact on the validity range of advanced fluid‐neutral models. Contributions to Plasma Physics, 60(5-6), e201900147. \newline \newline 
    Introduction of separate neutral energy equation for the AFN model inside SOLPS-ITER.
    \item Van Uytven, W., Dekeyser, W., Blommaert, M., Carli, S., \& Baelmans, M. (2022). Assessment of advanced fluid neutral models for the neutral atoms in the plasma edge and application in ITER geometry. Nuclear Fusion, 62(8), 086023. \newline \newline 
    AFN models in unstructured version of SOLPS-ITER, density scan of slab cases and ITER cases, introduction of flux limiters and automated selection between diffusion and Maxwellian approach.
    \item Van Uytven, W., Dekeyser, W., Blommaert, M., Horsten, N., \& Baelmans, M. (2022). Effect of drifts and currents on the validity of a fluid model for the atoms in the plasma edge. Nuclear Materials and Energy, 33, 101255. \newline \newline 
    First benchmark between AFN and EIRENE in the presence of drifts.
    \item Horsten, N. (2019). Fluid and hybrid fluid-kinetic models for the neutral particles in the plasma edge of nuclear fusion devices. \newline \newline 
    PhD manuscript N. Horsten
    \item Van Uytven, W. (2023). Development of Fluid and Hybrid Fluid-Kinetic Atom Models for Plasma Boundary Simulations and Assessment in Reactor-Relevant Conditions \newline \newline 
    PhD manuscript W. Van Uytven
\end{itemize}